---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# L2TWordLists 

[![Travis-CI Build Status](https://travis-ci.org/LearningToTalk/L2TWordLists.svg?branch=master)](https://travis-ci.org/LearningToTalk/L2TWordLists)

The goal of L2TWordLists is to provide some convenient high-level functions for
working with Eprime files produced by our real-word repetition and non-word
repetition experiments.

## Installation

Install L2TWordLists from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("LearningToTalk/L2TWordLists")
```

## Usage

Parse an Eprime file to get trial-level information:

```{r}
library(dplyr, warn.conflicts = FALSE)
library(L2TWordLists)

test_file <- "./tests/testthat/test-files/TimePoint3/RealWordRep_008L54MS5.txt"

# Parse Eprime file
df_trials <- get_rwr_trial_info(test_file)
df_trials
```

Create a WordList table using that trial-level information:

```{r}
df_wordlist <- lookup_rwr_wordlist(df_trials)
df_wordlist
```

Save a read-only copy of a WordList table:

```{r, eval = TRUE}
# Save wordlist to a temporary file
outpath <- tempfile("my-wordlist", fileext = ".txt")
write_protected_tsv(df_wordlist, outpath)

# mode is `444` when a file is read-only
file.info(outpath)[["mode"]]

# returns -1 when write permissions are unavailable
unname(file.access(outpath, 2))
```


### Create a WordList from a Participant ID

```{r, echo = FALSE, message = FALSE}
# Clean up any leftovers from last time
"./tests/testthat/mock-analysis/RealWordRep/TimePoint1/WordLists/" %>% 
  list.files(full.names = TRUE) %>% 
  unlink(force = TRUE)
```

The function `create_rwr_wordlist_file()` is a shortcut that will create a 
WordList for a particular participant. This function replicates the main 
functionality of our older R scripts. All the user needs to provide is a
participant ID, a study name, and a task directory.

```{r}
# Using a mock location for the package documentation...
task_dir <- "./tests/testthat/mock-analysis/RealWordRep"
study_name <- "TimePoint1"
participant_id <- "001L"

create_rwr_wordlist_file(participant_id, study_name, task_dir)
```

By default, the function will not overwrite a WordList.

```{r, error = TRUE}
create_rwr_wordlist_file(participant_id, study_name, task_dir)
```

We can update a WordList with `update = TRUE`, however:

```{r}
create_rwr_wordlist_file(participant_id, study_name, task_dir, update = TRUE)
```

If we set the participant ID to a blank `""`, then the function will **create a
WordList for every participant ID in a study** folder.

```{r}
create_rwr_wordlist_file("", study_name, task_dir, update = TRUE)
```

The function invisibly returns a list with the generated WordList and the file 
location. That is, we can run the function by itself and not see the generated
WordList printed out --- this prevents the console from being flooded with
data-frame print-outs. But we can assign the results of the function to a
variable and see the WordList data and file locations. In this case, two 
WordsLists have been updated:

```{r}
results <- create_rwr_wordlist_file("", study_name, task_dir, update = TRUE)
str(results)
```

```{r, echo = FALSE, message = FALSE}
# Clean up
"./tests/testthat/mock-analysis/RealWordRep/TimePoint1/WordLists/" %>% 
  list.files(full.names = TRUE) %>% 
  unlink(force = TRUE)
```


## Packaged stimulus information

Tables of stimulus information about the items in our word-repetition
experiments are bundled with the package and accessible with `l2t_wordlists`.

Default forms of the list are stored by Task and TimePoint, and custom one-off
lists are stored in a separate list.

```{r}
l2t_wordlists
```


## Test data coverage

```{r, echo = FALSE, message = FALSE}
list_files <- function(...) {
  list.files(..., full.names = TRUE, recursive = TRUE)
}

df_eprime <- data_frame(
 Eprime_Path = list_files(testthat::test_path("test-files"), pattern = ".txt"),
 Study = basename(dirname(Eprime_Path)),
 Eprime_Basename = basename(Eprime_Path) %>% tools::file_path_sans_ext(),
 Task = stringr::str_extract(Eprime_Basename, "^.+WordRep"))

df_exp_info <- df_eprime$Eprime_Path %>% 
  lapply(get_rwr_trial_info) %>% 
  bind_rows() %>% 
  group_by(TimePoint, Dialect, Experiment, Eprime.Basename) %>% 
  summarise(NumTrials = n()) %>% 
  ungroup %>% 
  rename(ExperimentName = Experiment, Eprime_Basename = Eprime.Basename)

df_test_info <- df_eprime %>% 
  left_join(df_exp_info) %>% 
  select(Task, Study, Dialect, ExperimentName, NumTrials) %>% 
  distinct() %>% 
  arrange(Task, Study, Dialect, ExperimentName, desc(NumTrials)) 
```


We created our WordList tables using an incrementally developed suite of R 
scripts. These original WordList tables are used to validate the behavior of 
this package by comparing the original tables against the ones generated by this
package. These tests are in the `tests` folder. 

The testing data was selected to use all available combinations of dialect,
experiment name (i.e., the name of the Eprime executable that generated the
output), and trial counts among our collected data. The table belows shows each
of the combinations of dialect, experiment name, and trial counts that are
tested in this package. 

```{r, echo = FALSE}
knitr::kable(df_test_info)
```


The build status badge at the top of this page indicates whether the package 
successfully passed all these tests (and also passed the standard checks for R
packages).


