---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# L2TWordLists 

[![Travis-CI Build Status](https://travis-ci.org/LearningToTalk/L2TWordLists.svg?branch=master)](https://travis-ci.org/LearningToTalk/L2TWordLists)

The goal of L2TWordLists is to provide some convenient high-level functions for
working with Eprime files produced by our real-word repetition and non-word
repetition experiments.

## Installation

Install L2TWordLists from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("LearningToTalk/L2TWordLists")
```

## Usage

Parse an Eprime file to get trial-level information:

```{r}
library(dplyr, warn.conflicts = FALSE)
library(L2TWordLists)

test_file <- "./tests/testthat/test-files/TimePoint3/RealWordRep_008L54MS5.txt"

# Parse Eprime file
df_trials <- get_rwr_trial_info(test_file)
df_trials
```

Create a WordList table using that trial-level information:

```{r}
lookup_rwr_wordlist(df_trials)
```

## Test data coverage


```{r, echo = FALSE, message = FALSE}
list_files <- function(...) {
  list.files(..., full.names = TRUE, recursive = TRUE)
}

df_eprime <- data_frame(
 Eprime_Path = list_files(testthat::test_path("test-files"), pattern = ".txt"),
 Study = basename(dirname(Eprime_Path)),
 Eprime_Basename = basename(Eprime_Path) %>% tools::file_path_sans_ext(),
 Task = stringr::str_extract(Eprime_Basename, "^.+WordRep"))

df_exp_info <- df_eprime$Eprime_Path %>% 
  lapply(get_rwr_trial_info) %>% 
  bind_rows() %>% 
  group_by(TimePoint, Dialect, Experiment, Eprime.Basename) %>% 
  summarise(NumTrials = n()) %>% 
  ungroup %>% 
  rename(ExperimentName = Experiment, Eprime_Basename = Eprime.Basename)

df_test_info <- df_eprime %>% 
  left_join(df_exp_info) %>% 
  select(Task, Study, Dialect, ExperimentName, NumTrials) %>% 
  distinct() %>% 
  arrange(Task, Study, Dialect, ExperimentName, desc(NumTrials)) 
```


We created our WordList tables using an incrementally developed suite of R 
scripts. These original WordList tables are used to validate the behavior of 
this package by comparing the original tables against the ones generated by this
package. These tests are in the `tests` folder. 

The testing data was selected to use all available combinations of dialect,
experiment name (i.e., the name of the Eprime executable that generated the
output), and trial counts among our collected data. The table belows shows each
of the combinations of dialect, experiment name, and trial counts that are
tested in this package. 

```{r, echo = FALSE}
knitr::kable(df_test_info)
```


The build status badge at the top of this page indicates whether the package 
successfully passed all these tests (and also passed the standard checks for R
packages).

## Packaged stimulus information

Tables of stimulus information about the items in our word-repetition
experiments are bundled with the package and accessible with `l2t_wordlists`.

Default forms of the list are stored by Task and TimePoint, and custom one-off
lists are stored in a separate list.

```{r}
l2t_wordlists
```

