---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# L2TWordLists 

[![Travis-CI Build Status](https://travis-ci.org/LearningToTalk/L2TWordLists.svg?branch=master)](https://travis-ci.org/LearningToTalk/L2TWordLists)

The goal of L2TWordLists is to provide some convenient high-level functions for
working with Eprime files produced by our real-word repetition and non-word
repetition experiments.

## Installation

Install L2TWordLists from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("LearningToTalk/L2TWordLists")
```

## Packaged stimulus information

Tables of stimulus information about the items in our word-repetition
experiments are bundled with the package and accessible with `l2t_wordlists`.

Default forms of the list are stored by Task and TimePoint, and custom one-off
lists are stored in a separate list.

```{r}
library(dplyr, warn.conflicts = FALSE)
library(L2TWordLists)

l2t_wordlists
```


## Usage

Parse an Eprime file to get trial-level information:

```{r}
test_file <- "./tests/testthat/test-files/TimePoint3/RealWordRep_008L54MS5.txt"

# Parse Eprime file
df_trials <- get_rwr_trial_info(test_file)
df_trials
```

Create a WordList table using that trial-level information:

```{r}
lookup_rwr_wordlist(df_trials)
```
